Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Add more figure

\begin{figure}[h]
\centering
\begin{subfigure}[b]{.4\textwidth}
  \texttt{Video ID: ArzhjEk4j\_Y \\
  Activity: Building sandcastles \\
  \\
  Prediction: \\
  0.7896	Building sandcastles \\
  0.0073	Doing motocross \\
  0.0049	Beach soccer \\}
\end{subfigure}%
\begin{subfigure}[b]{.6\textwidth}
  \centering
\includegraphics[width=0.95\linewidth]{img/results_visualization_classification_1}
\end{subfigure}
\caption{Example of activity classification.}
\label{fig:example_results_classification}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\begin{subfigure}[b]{.5\textwidth}
    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_1}
    \texttt{Video ID: ArzhjEk4j\_Y \\
    Ground Truth: Building sandcastles \\
    \\
    Prediction: \\
    0.7896	Building sandcastles \\
    0.0073	Doing motocross \\
    0.0049	Beach soccer \\}
\end{subfigure}%
\begin{subfigure}[b]{.5\textwidth}
    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_4}
    \texttt{Video ID: VrNHEv6aR38 \\
    Ground Truth: Playing water polo \\
    \\
    Prediction: \\
    0.7645	Playing water polo \\
    0.2018	Swimming \\
    0.0065	Springboard diving\\}
\end{subfigure}

\caption{Examples of activity classification.}
\label{fig:example_results_classification}
\end{figure}
